### 2018-01-31 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Notes Update

@@

>>>>

\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}

\usepackage{mathtools}

\newtagform{brackets}{[}{]}
\usetagform{brackets}

@@

\subsubsection{Trigonometric f(x)}
General forms:\\
If $f(x)=m\cos\omega x$
$$PI: \ y=P\cos\omega x+Q\sin\omega x$$
If $f(x)=n\sin\omega x$
$$PI: \ y=P\cos\omega x+Q\sin\omega x$$
If $f(x)=m\cos\omega x\pm n\sin\omega x$
$$PI: \ y=P\cos\omega x+Q\sin\omega x$$
\paragraph{$f(x)=m\sin\omega x$ or $n\sin\omega x$}
$f(x)=13\sin4x$
$$PI: \ y=P\cos\omega x+Q\sin\omega x$$
$$\frac{dy}{dx}=-\omega P\sin\omega x+\omega Q\cos\omega x$$
$$\frac{d^2y}{dx^2}=-\omega^2P\cos\omega x-\omega^2Q\sin\omega x$$
$$\textcolor{red}{\frac{d^2y}{dx^2}-5\frac{dy}{dx}+6y=13\sin3x}$$
$$-\omega^2P\cos\omega x-\omega^2Q\sin\omega x-5(-\omega P\sin\omega x+\omega Q\cos\omega x)+6(P\cos\omega x+Q\sin\omega x)=13\sin3x$$
Equate cos terms
$$-\omega^2 P\cos\omega x-5\omega Q\cos\omega x+6P\cos\omega x=0$$
Substitute $\omega=3$ and divide by $\cos3x$
$$-9P-15Q+6P=0$$
Simplify
\begin{equation}\label{eq:cos}
-3P-15Q=0
\end{equation}
Equate $\sin$ terms
$$-\omega^2Q\sin\omega x+5\omega P\sin\omega x+6Q\sin\omega x=13\sin3x$$
Substitute $\omega=3$ and divide by $\sin3x$
$$-9Q+15P+6Q=13$$
Simplify
\begin{equation}\label{eq:sin}
15P-3Q=13
\end{equation}
Multiply \eqref{eq:cos} by 5
$$-15P-75Q=0$$
Add the multiplied \eqref{eq:cos} and \eqref{eq:sin}
$$-78Q=13$$
Simplify
$$Q=-\frac{1}{6}$$
Substitute to find P
$$15\times\frac{1}{6}=-3P \quad P=\frac{5}{6}$$
Substitute and add to the CF to find the PI
$$y=Ae^{3x}+Be^{2x}+\frac{5}{6}\cos3x-\frac{1}{6}\sin3x$$
